---
title: "Exclusion flowcharts"
output: github_document
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE) #defines default echo (display code)
knitr::opts_chunk$set(eval = TRUE) #defines default eval (display result of code)
knitr::opts_chunk$set(comment = "") # no space/character before results (e.g. in tables)
knitr::opts_chunk$set(tidy = T) # let r reformat your code to look tidy in the output
knitr::opts_chunk$set(collapse = F) # should code and results be shown in the same chunk (=T) or be split in several chunks in the document (=F)
```

The aim of this script is to make exclusion flowcharts for different clinical scenarios and outcomes. The number of patients in each group is copied from a secure server for sensitive data (not available here). Start by loading the library.

```{r libraries}
library(PRISMAstatement)
```

Next, make an exclusion flowchart for the **base clinical model with overall survival** as outcome:

```{r base clinical OS}
flow_exclusions(
    incl_counts = c(1736, 1589, 1564, 1447),
    total_label = "Total Screened",
    incl_labels = c("Curative setting", "Early disease or locoregionally advanced disease", "Outcome available"),
    excl_labels = c("Recurrence/Metastatic setting", "Metastatic disease", "Missing outcome"),
    percent_of_total = TRUE
  )

```

Similarly for the **base clinical model with disease-free survival** as outcome:

```{r base clinical dfs}
flow_exclusions(
    incl_counts = c(1736, 1589, 1564, 1251),
    total_label = "Total Screened",
    incl_labels = c("Curative setting", "Early disease or locoregionally advanced disease", "Outcome available"),
    excl_labels = c("Recurrence/Metastatic setting", "Metastatic disease", "Missing outcome"),
    percent_of_total = TRUE, labelloc="t", label="test"
  )

```

Next the flowchart for **GS1, GS2 and GS3 and overall survival**. These use the same subset of data, but GS3 has different variable encoding. 

### STOPPED

```{r GS1 GS2 GS3 OS}
flow_exclusions(
    incl_counts = c(1736, 1589, 1564, 1251),
    total_label = "Total Screened",
    incl_labels = c("Curative setting", "Early disease or locoregionally advanced disease", "Outcome available"),
    excl_labels = c("Recurrence/Metastatic setting", "Metastatic disease", "Missing outcome"),
    percent_of_total = TRUE, labelloc="t", label="test"
  )

```


